### 2020-11-09 written/SC_model/SC_model.tex
sc model stuff
sc update

We ran EPI to obtain SC model connectivity parameters $z$ producing rapid task switching (Fig. \ref{fig:SC}C).
There is strong pairwise correlation between each parameter of the connectivity matrix.
Shading the distribution by $p_P$, we see that positive shifts in the parameters result in lower accuracy in the Pro task.
Indeed, this difference in accuracy is apparent when we simulate this model for greater parameter values (black star) and lower parameter values (gray star) (Fig. \ref{fig:SC}D).

To make sense of this inferred distributions, we followed the approach of Duan et al. by decomposing the connectivity matrix $W = V\Lambda V^{-1}$ in such a way (the Schur decomposition) that the basis vectors $v_i$ are the same for all $W$ (Fig. SX). 
These basis vectors have intuitive roles in processing for this task, and are accordingly named the \textit{all} mode - all neurons co-fluctuate, \textit{side} mode - one side dominates the other, \textit{task} mode - the Pro or Anti populations dominate the other, and \textit{diag} mode - Pro- and Anti-populations of opposite hemispheres dominate the opposite pair. 
The corresponding eigenvalues (e.g. $\lambda_{\text{task}}$, which change according to $W$) indicate the degree to which activity along that mode is increased or decreased by $W$. 
We found that $\lambda_{\text{all}}$ is anti-correlated with $p_P$ and $\lambda_{\text{task}}$ is correlated with $p_P$.
TODO interpret further.  Maybe push further on the optogenetics analysis.

@@

>>>>

We ran EPI to obtain SC model connectivity parameters $z$ producing rapid task switching (Fig. \ref{fig:SC}C).
There is strong pairwise correlation between each parameter of the connectivity matrix.
To make sense of this inferred distribution, we followed the approach of Duan et al. by decomposing the connectivity matrix $W = V\Lambda V^{-1}$ in such a way (the Schur decomposition) that the basis vectors $v_i$ are the same for all $W$ (Fig. \ref{fig:SC_Eigs}A). 
These basis vectors have intuitive roles in processing for this task, and are accordingly named the \textit{all} mode - all neurons co-fluctuate, \textit{side} mode - one side dominates the other, \textit{task} mode - the Pro or Anti populations dominate the other, and \textit{diag} mode - Pro- and Anti-populations of opposite hemispheres dominate the opposite pair. 
The corresponding eigenvalues (e.g. $\lambda_{\text{task}}$, which change according to $W$) indicate the degree to which activity along that mode is increased or decreased by $W$. 
Strong anticorrelation between $p_P$ and $\lambda_{\text{all}}$ (Fig. \ref{fig:SC_Eigs}B) suggests that accuracy in the Pro task is greater when all parameters decrease along the strongly correlated posterior.
Indeed, this difference in accuracy is apparent when we simulate this model for greater parameter values (black star) and lower parameter values (gray star) (Fig. \ref{fig:SC}D). 
In contrast, intermediate parameter values result in greater $p_A$ than extremal parameter vaues (Fig. \ref{fig:SC_EPI2}).
While $p_P$ is well predicted by the remaining Schur eigenvalues (correlated with $\lambda_{\text{task}}$ and $\lambda_{\text{diag}}$ and anticorrelated with $\lambda_{\text{side}}$), $p_A$ is not well predicted by any of them (Fig. \ref{fig:SC_Eigs}B).

Finally, we sought to

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.75]{figs/figSX1.pdf}
\end{center}
\caption{\small Sentence 1 .
A. Rapid task switching behavioral paradigm (see text). 
B. blah}
\label{fig:SC_Eigs}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.75]{figs/figSX2.pdf}
\end{center}
\caption{\small Sentence 1 .
A. Rapid task switching behavioral paradigm (see text). 
B. blah}
\label{fig:SC_EPI2}
\end{figure}
